%   Copyright 2016 Ahmet Arslan
%
%   Licensed under the Apache License, Version 2.0 (the "License");
%   you may not use this file except in compliance with the License.
%   You may obtain a copy of the License at
%
%       http://www.apache.org/licenses/LICENSE-2.0
%
%   Unless required by applicable law or agreed to in writing, software
%   distributed under the License is distributed on an "AS IS" BASIS,
%   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%   See the License for the specific language governing permissions and
%   limitations under the License.

\newpage
\doublespacing

\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\begin{center}{\textbf{ACKNOWLEDGMENTS}}\end{center}

I would like to express my sincerest gratitude to my supervisor, Associate Professor Dr. Bekir Taner Din\c{c}er, who has supported me throughout my dissertation with his patience and unsurpassed knowledge. I thank him for his guidance and encouragement, where good advice, support, and friendship has been invaluable on both academic and personal levels.

Also, I would like to thank Professor Dr. \"{U}mit Deniz Turan, Associate Professor Dr. Cihan Kaleli, Assistant Professor Dr. Kemal \"{O}zkan and Assistant Professor Dr. Mehmet Ko\c{c} on my dissertation committee for their valuable contributions. \\

\noindent
Finally, I dedicate this PhD dissertation to \texttt{the projects} from which I came\ldots  \\

\begin{flushright}
Ahmet ARSLAN \\  August, 2016
\end{flushright}

\vspace{7.2cm} 

\noindent
{\small This work is supported by T\"{U}B\.{I}TAK, scientific and technological research projects funding program, under grant 114E558. Any opinions, findings and conclusions or recommendations expressed in this material are the author's and do not necessarily reflect those of the sponsor.}